---
title: "03-stratified_hba1cgp"
author: "Yayin Chang"
date: "2023-08-28"
output: html_document
---


```{r echo=FALSE, message=FALSE, warning=FALSE}

#source("~/Desktop/work/cofit/rd/01r/diabetes_mellitus/config.R")
source("~/Desktop/work/cofit/rd/01r/diabetes_mellitus/r_script/stratified.R")
#gridExtra::grid.arrange(grobs = combined_plot)
```

**依據糖化血色素改善成效進行分層分析，分成三個組別：**

-   **成效「優異」: ∆HbA1c_conv \>= -1.92**
-   **「良好」: -1.92 \> ∆HbA1c_conv \>= -0.87**
-   **「低於預期」: \> ∆HbA1c_conv \> -0.87 )**

```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.width= 12, fig.height=8}
library(ggpubr)

# Create an empty list to store all group plot lists
all_group_plot_lists <- list()

plot_groups <- list(
stat.var.profile,
stat.var.diet,
stat.var.blood.base,
stat.var.blood.end,
stat.var.blood.delta,
stat.var.blood.delta.pt,
stat.var.inbody.base,
stat.var.inbody.end,
stat.var.inbody.delta,
stat.var.inbody.delta.pt
)

names(plot_groups) <- c(
"stat.var.profile",
"stat.var.diet",
"stat.var.blood.base",
"stat.var.blood.end",
"stat.var.blood.delta",
"stat.var.blood.delta.pt",
"stat.var.inbody.base",
"stat.var.inbody.end",
"stat.var.inbody.delta",
"stat.var.inbody.delta.pt")

for (group_name in names(plot_groups)) {

  group_plots <- plot_groups[[group_name]]

  # Create a list to store plots within the group
  group_plot_list <- list()
  
  for (plot_name in group_plots) {
    
    group_plot_list[[plot_name]] <- plot_collection[[plot_name]]
  }

  # Combine plots within the same group and arrange them in 2 columns
  combined_group_plot <- ggarrange(plotlist = group_plot_list, ncol = 2)
  
  # Store the combined group plot list
  all_group_plot_lists[[group_name]] <- combined_group_plot
  group_plot_list<-list()

  #cat("\n")
}

```

### 初始狀態(Baseline) {#dm_baseline .unnumbered}

#### Inbody {#dm_inbody_inbody .unnumbered}

```{r }
all_group_plot_lists["stat.var.inbody.base"]
```

#### Blood {#dm_blood_baseline .unnumbered}

```{r }
all_group_plot_lists["stat.var.blood.base"]
```

### 飲食(Diet) {#dm_diet_baseline .unnumbered}

```{r }
all_group_plot_lists["stat.var.diet"]
```

### 介入後狀態(Endpoint) {#dm_endpoint .unnumbered}

#### Inbody {#dm_inbody_endpoint .unnumbered}

```{r }
all_group_plot_lists["stat.var.inbody.end"]
```

#### Blood {#dm_blood_endpointe .unnumbered}

```{r }
all_group_plot_lists["stat.var.blood.end"]
```

### ∆成效(Effectiveness) {#dm_delta .unnumbered}

#### Inbody

```{r }
all_group_plot_lists["stat.var.inbody.delta"]
```

#### Blood

```{r }
all_group_plot_lists["stat.var.blood.delta"]
```

### ∆成效(%)(Effectiveness) {#dm_delta_pt .unnumbered}

#### Inbody

```{r }
all_group_plot_lists["stat.var.inbody.delta.pt"]
```

#### Blood

```{r }
all_group_plot_lists["stat.var.blood.delta.pt"]
```
